%-------------------------
% Resume in LaTeX
% Author : Hugo Prado Serafim Pereira
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

% Add color package and define a custom color
\usepackage{xcolor}
\definecolor{myblue}{RGB}{25, 25, 112} % A professional RoyalBlue color

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\color{myblue} \Huge \scshape Hugo Prado Serafim Pereira} \\ \vspace{1pt}
  \small \href{mailto:hugop.dev@gmail.com}{\underline{hugop.dev@gmail.com}} $|$ 
  \href{https://www.linkedin.com/in/hugopradops/}{\underline{linkedin.com/in/hugopradops}} $|$
  \href{https://github.com/hugopradops}{\underline{github.com/hugopradops}} $|$
  \href{tel:+12048806453}{\underline{+1 (204) 880-6453}}
\end{center}

%-----------ABOUT ME-----------------
\section{About Me}
  A \textbf{Computer Science student} passionate about building innovative software solutions, with a strong foundation in programming and problem-solving. Currently seeking an \textbf{internship} or a \textbf{junior developer role} to apply my skills, contribute to impactful projects, and gain hands-on experience in the tech industry.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Guelph}{Guelph, ON, Canada}
      {Bachelor of Science in Computer Science (Expected Graduation: 2027)}{}
  \resumeSubHeadingListEnd

%-----------PERSONAL PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Brazilian Food Store Template}{Developed a responsive web template for a Brazilian food store using \textbf{React} and \textbf{Next.js}.}
    \resumeSubItem{AI Learning Homelab}{Set up and deployed the \textbf{Gemma3:12b} AI model on a homelab environment using \textbf{Traefik}, \textbf{Docker}, and \textbf{SQLite} for backend management.}
    \resumeSubItem{Personal Website}{Built a portfolio website to showcase projects, skills, and experience using \textbf{Vite}, \textbf{TypeScript}, \textbf{React}, and \textbf{Tailwind CSS}.}
  \resumeSubHeadingListEnd
  All projects are hosted on my homelab using Docker and Traefik for reverse proxy management. Live links are available on my personal website at \href{https://hub.hugoprado.dev/}{\underline{hub.hugoprado.dev}}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{Programming Languages}{C, Java, JavaScript, Python, HTML, CSS, TypeScript}
    \resumeItem{Frameworks and Libraries}{React, Next.js, Node.js, Express.js}
    \resumeItem{Databases}{SQLite, SQL, MongoDB}
    \resumeItem{Tools and Technologies}{Docker, JSON, YAML, Gradle, Traefik, Postman, GitHub Actions, Git, GitHub}
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
  \resumeSubHeadingListStart
    \resumeSubItem{CIS*3750 - System Analysis and Design in Applications}{Gained experience designing and analyzing software systems with a focus on real-world applications.}
    \resumeSubItem{CIS*3490 - Analysis and Design of Computer Algorithms}{Studied algorithm efficiency, complexity analysis, and optimization techniques.}
    \resumeSubItem{CIS*2750 - Software System Development and Integration}{Learned to design and integrate software systems, emphasizing teamwork and project management.}
    \resumeSubItem{CIS*2520 - Data Structures}{Explored data structures like linked lists, trees, and graphs, and their applications in software development.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Previous Work and Volunteer Experience}
  \resumeSubHeadingListStart
    % Volunteer Experience
    \resumeSubheading
      {Tutor (Volunteer)}{Winnipeg, MB, Canada}
      {Grant Park High School}{}
      \resumeItemListStart
        \item Volunteered as a tutor for exchange students, helping them succeed academically while completing over 50 hours of service.
      \resumeItemListEnd

    % Professional Experience
    \resumeSubheading
      {Food Services Team Member}{Winnipeg, MB, Canada}
      {Assiniboine Park Zoo}{}
      \resumeItemListStart
        \item Collaborated with team members to deliver exceptional service in a fast-paced environment.
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}