%-------------------------
% Resume in LaTeX
% Author : Hugo Prado Serafim Pereira
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & \small #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{myblue}{RGB}{25, 25, 112}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\color{myblue} \Huge \scshape Hugo Prado} \\ \vspace{1pt}
  \small
  \href{mailto:hugop.dev@gmail.com}{\underline{hugop.dev@gmail.com}} $|$
  \href{https://www.hugoprado.dev}{\underline{hugoprado.dev}} $|$
  \href{https://www.linkedin.com/in/hugopradops/}{\underline{linkedin.com/in/hugopradops}} $|$
  \href{https://github.com/hugopradops}{\underline{github.com/hugopradops}}
\end{center}

%-----------ABOUT ME-----------------
\section{About Me}
  \small{Hardworking Computer Science student based in Kitchener, ON, Canada, seeking a junior or new graduate software developer position. Passionate about building and self-hosting full-stack applications, with hands-on experience across the entire development lifecycle.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Guelph}{Guelph, ON, Canada}
      {Bachelor of Computing (B.Comp.) in Computer Science}{Expected Oct 2026}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \small{All projects self-hosted on a homelab (3 machines, Proxmox, Docker, Traefik, Cloudflare Tunnels). See all projects and more about me at \href{https://www.hugoprado.dev}{\underline{hugoprado.dev}}.}
  \vspace{-2pt}
  \resumeSubHeadingListStart
    \resumeSubItem{WatchMage \textnormal{-- \href{https://watchmage.hugoprado.dev}{\underline{watchmage.hugoprado.dev}}} \textnormal{$|$ \emph{Next.js, TypeScript, React}}}{Mage-themed PC gaming tracking dashboard with dynamic data display and responsive UI.}
    \resumeSubItem{Job Application Tracker \textnormal{-- \href{https://demo-job-tracker.hugoprado.dev}{\underline{demo-job-tracker.hugoprado.dev}}} \textnormal{$|$ \emph{React, FastAPI, PostgreSQL, Docker}}}{Full-stack self-hosted tracker to manage job search pipeline from applied to offer.}
    \resumeSubItem{Rustic Notes \textnormal{$|$ \emph{Rust, TUI}}}{Cross-platform terminal notes app as a faster alternative to PICO/NANO with an improved UI.}
    \resumeSubItem{toremember.gift \textnormal{-- \href{https://www.toremember.gift}{\underline{toremember.gift}}} \textnormal{$|$ \emph{In Progress}}}{E-commerce site for a family 3D printing business, migrating from Facebook Marketplace.}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{Languages}{JavaScript, TypeScript, Python, Rust, C, Java, SQL, HTML, CSS, Bash}
    \resumeItem{Frameworks \& Libraries}{React, Next.js, Node.js, Express.js, Tailwind CSS, FastAPI}
    \resumeItem{Databases}{PostgreSQL, SQLite, MongoDB}
    \resumeItem{Developer Tools}{Git, GitHub, GitHub Actions, Docker, Postman, Gradle}
    \resumeItem{Infrastructure}{Proxmox, Traefik, Cloudflare Tunnels, Dokploy, Linux server administration}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {3D Printing Business}{Kitchener, ON, Canada}
      {toremember.gift -- Family-run Personalized Gifts \& Keepsakes}{}
      \resumeItemListStart
        \item\small{Assisted a family-run 3D printing business alongside studies: handled machine maintenance, multi-material printing, order fulfillment, and deliveries.}
        \item\small{Building a dedicated e-commerce website to help transition the business from Facebook Marketplace to an online storefront.}
      \resumeItemListEnd

    \resumeSubheading
      {Food Services Team Member}{Winnipeg, MB, Canada}
      {Assiniboine Park Zoo}{}
      \resumeItemListStart
        \item\small{Delivered service in a fast-paced, high-volume environment, adapting to different roles daily.}
      \resumeItemListEnd

    \resumeSubheading
      {Tutor (Volunteer)}{Winnipeg, MB, Canada}
      {Grant Park High School}{}
      \resumeItemListStart
        \item\small{Tutored exchange students for over 50 hours, helping them succeed academically.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RELEVANT COURSEWORK-----------
\section{Relevant Coursework}
  \vspace{2pt}
  \small{
    Data Science $\cdot$
    Software Engineering $\cdot$
    System Analysis \& Design $\cdot$
    Intro to Intelligent Systems $\cdot$
    Analysis \& Design of Algorithms $\cdot$
    Software System Dev \& Integration $\cdot$
    Data Structures $\cdot$
    Object Oriented Programming
  }

%-------------------------------------------
\end{document}